---
title: "Project: Which CPU?"
author: "AC"
output: ioslides_presentation
---

## About the Application

The Web Application uses the record of the relative performance measure and characteristics of 209 CPUs with a list of its specifications from the CPUS dataset of the MASS library.

When you select the specifications you want, the data about those CPUs that meet the specifications is shown in the RESULTS tab. 

After that, on another tab, PERFORMANCE, the comparitive plot of expected and published performance of these CPUs is shown.

## About the Variables

```{r}
# Name: Manufacturer and Model

# Cycle Time: In Nanoseconds

# Min and Max Memory: Minimum and Maximum Main Memory in KiloBytes

# Cache Size: In KiloBytes

# Min and Max Channels: Minimum and Maximum Number of Channels

# Performance: Published Performance on a Benchmark Mix Relative 
# to an IBM 370/158-3

# Estimated Performance: Estimated Performance (by Ein-Dor & 
# Feldmesser)
```


## Embedded R Code: Exploring Variables
```{r}
# Code for Variable Exploration
library(MASS)
library(knitr)
data("cpus")
s <- apply(cpus[,2:8], 2, range)
row.names(s) <- c("Lowest", "Highest")
colnames(s) <- c("Cycle Time", "Min Memory", "Max Memory", "Cache 
Size", "Min Channels", "Maximum Channels", "Performance")
kable(s, format = "html")
```

## The Web Application

1. Shiny App : <a href="https://abhijeetc.shinyapps.io/cpuperf/">Web App on CPUs</a>
2. Server and UI files: <a href="https://github.com/acmacy/CPU-Specifications">Github Repo</a>

Thank You for Visiting.


